\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
Explain hover target resize flickering better

More dangerously, it becomes easy to create an infinite loop. Suppose an
element shrinks on hover. Suppose the cursor hovers on the element,
which is then replaced by a smaller element, so the cursor is no longer
hovering on the element. Then the original element is put back, but is
now being hovered on! This condition manifests itself as flickering
between the two elements. It is unavoidable in any language or system
that allows hover targets to change size in response to hover events.

>>>>

More dangerously, it becomes easy to create an infinite loop. Suppose an element
shrinks on hover and returns to its original size without hover. Now suppose the
cursor hovers on the element, which is then replaced by a smaller element, so
the cursor is no longer hovering on the element. Then the original element is
put back, but is now being hovered on because the mouse has not moved, so the
cycle repeats. This condition often manifests itself as flickering between the
two elements. As this description is implementation-independent, it is
unavoidable in any language or system that allows hover targets to change size
in response to hover events on that target.
